Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-20 article.tex
updates

Molecular mechanics models molecular systems using force fields in classical mechanics. Three approximations were made to reduce the computational
 complexity. Each atom is simulated as one particle; each particle has their designated attributes including radius, Polaris ability and net charge;
 and international are treated as springs with an equilibrium distance same as bond length. Essentially this theory simulates every element of the
 molecular system as if it were fixed particles connected by strings, which hugely reduces the computational complexity.

@@

We now return to the theory of molecular mechanics, it is not exactly accurate since it is restricted by parameters of equations, i.e. difference
force fields for different atoms. A similar and perhaps more comprehensible explanation can be made from the theory of renormalisation group.
While decreasing the parameters of calculation and reducing computation time, the accuracy of the result is decreasing as well. Molecular mechanics
 does the same for force fields and interactions inside the atom.

@@

\section{Non-technical background}
In any quantum computing processes, the building blocks of the process are qubits. A qubit, or quantum bit, is the quantum analogue of the classical
 bit (strings of zeros and ones). So the qubit represents a quantum superposition or combination of a predetermined ‘0’ and a ‘1’ state. The quantum
  algorithms were run on superconducting qubits, these are a physical realisation of quantum bits based upon what are known as superconducting
  interference devices (SQUIDs), and attempt to find properties of the wavefunction of the molecule (in this case molecular Hydrogen).

@@

One of the reasons that developing new approaches to tackling electronic structure calculations are of importance is that they are extremely
computationally expensive. Indeed one of the original motivations for the field of quantum computing was the desire to simulate quantum systems
 in nature by using quantum systems. A prominent driving factor in the interest in and development of quantum computing is the aim to create quantum
  hardware and software that will allow for efficient quantum simulations of chemical systems. A problem of tantamount importance in quantum chemistry
  is that of finding the lowest energy eigenvalue of molecular electronic structures. These energy eigenvalues define a great deal of properties of
  interest in the molecule. This is of great interest in for example the development of pharmaceuticals where companies have an extremely laborious
  testing and trials process, if a significant part of the initial testing process could be done in silico - this would represent significant savings
  and would better ensure that the pharmaceutical under development behaved as required prior to starting trials.

>>>>

Molecular mechanics models molecular systems using force fields in classical mechanics. Three approximations were made to reduce the computational
 complexity. Each atom is simulated as one particle; each particle has their designated attributes including radius, Polaris ability and net charge;
 and interactions are treated as springs with an equilibrium distance same as bond length. Essentially this theory simulates every element of the
 molecular system as if it were fixed particles connected by strings, which hugely reduces the computational complexity.

@@

We now return to the theory of molecular mechanics, it is not exactly accurate since it is restricted by parameters of equations, i.e. different
force fields for different atoms. A similar and perhaps more comprehensible explanation can be made from the theory of renormalisation group.
While decreasing the parameters of calculation and reducing computation time, the accuracy of the result is decreasing as well. Molecular mechanics
 does the same for force fields and interactions inside the atom.

@@

\section{Non-technical background}

In any quantum computing processes, the building blocks of the process are qubits. A qubit, or quantum bit, is the quantum analogue of the classical
 bit (strings of zeros and ones). So the qubit represents a quantum superposition or combination of a predetermined ‘0’ and a ‘1’ state. The quantum
  algorithms were run on superconducting qubits, these are a physical realisation of quantum bits based upon what are known as superconducting
  interference devices (SQUIDs), and attempt to find properties of the wavefunction of the molecule (in this case molecular Hydrogen).

@@

One of the reasons that developing new approaches to tackling electronic structure calculations is of importance is that they are extremely
computationally expensive. Indeed one of the original motivations for the field of quantum computing was the desire to simulate quantum systems
 in nature by using quantum systems. A prominent driving factor of the interest in and development of quantum computing is the aim to create quantum
 hardware and software that will allow for efficient quantum simulations of chemical systems. A problem of tantamount importance in quantum chemistry
 is that of finding the lowest energy eigenvalue of molecular electronic structures. These energy eigenvalues define a great deal of properties of
 interest in the molecule. This is of great interest in for example the development of pharmaceuticals where companies have an extremely laborious
 testing and trials process, if a significant part of the initial testing process could be done in silico - this would represent significant savings
 and would better ensure that the pharmaceutical under development behaved as required prior to starting trials.
